Hierarchical storage management for neuroimaging applications in user space

### 2023-08-08 paper/sea-neuro/paper-neuro.tex
Edits up to section 2.2

	Neuroimaging open-data initiatives have led to increased availability of large
  scientific datasets. While these datasets are shifting the processing
  bottleneck from compute-intensive to data-intensive, current standardized
  analysis tools have yet to adopt strategies that mitigate the costs
  associated with large data transfers \TG{use a word better than transfers}. A major challenge in adapting neuroimaging
  applications for data-intensive processing is that they must be entirely
  rewritten.

  To facilitate data management for standardized neuroimaging tools, we
  developed Sea, a library that intercepts and redirects application read and
  write calls to minimize data transfer time. In this paper, we investigate the
  performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  SPM and AFNI), using three neuroimaging datasets of different sizes
  (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  computing clusters. Our results demonstrate that given the features of the
  applications and datasets, Sea provides large speedups (up to 32$\times$) when
  the shared file system's (e.g. Lustre) performance is deteriorated. When the
  shared file system is not overburdened by other users, performance is
  unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  is minimal, as it can be used to limit files on PFS.
\end{abstract}
\begin{document}

@@

    \centering
    \includegraphics[width=\columnwidth]{figures/sea-diagram.pdf}%
\caption{The Sea data-management library overview}
\label{fig:seaneuro:diagram}
\end{figure*}
    Sea (Figure~\ref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls (more specifically, file access calls to the GNU C library,
    glibc) on Linux systems. This enables Sea to redirect write calls
    aimed at slower storage devices to a faster devices whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini}. This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. It is important to note that Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

@@

    As neuroimaging pipeline results typically require post-processing and
    HPC \TG{It'd be useful to add a sentence before explaining that neuroimaging applications typically run on HPC systems} compute-local resources are only accessible during the reserved
    duration, Sea provides functionality to flush and evict data to persistent
    shared storage. To avoid interrupting ongoing
    processing with data management operations, this is accomplished via a separate thread (known as the
    ``flusher'') that moves data from the caches to long-term storage. Users must inform Sea of files
    that need to be persisted to storage within a file called
    \texttt{.sea\_flushlist}, and temporary files which can be removed from
    cache within a file called the \texttt{.sea\_evictlist}. Both these files
    can be populated using regular expressions to denote the paths to flush and
    evict. If a file occurs in both the \texttt{.sea\_flushlist} and
    \texttt{.sea\_evictlist}, Sea will interpret this as a \texttt{move}
    operation and simply move the file from local to persistent storage rather
    than copying it. Files that will be reused by the application should only be
    flushed rather than flushed and evicted, as files can benefit from speedups
    related to reading from fast rather than slow storage. Sea currently also
    provides a rudimentary prefetch thread that can move files located within
    Sea to the fastest available cache. To use Sea's prefetch
    capabilities, a file called \texttt{.sea\_prefetchlist} needs to be
    populated using regular expressions like the flushing and eviction files.

>>>>

	Neuroimaging open-data initiatives have led to increased availability of large
  scientific datasets. While these datasets are shifting the processing
  bottleneck from compute-intensive to data-intensive, current standardized
  analysis tools have yet to adopt strategies that mitigate the costs
  associated with large data transfers. A major challenge in adapting neuroimaging
  applications for data-intensive processing is that they must be entirely
  rewritten. To facilitate data management for standardized neuroimaging tools, we
  developed Sea, a library that intercepts and redirects application read and
  write calls to minimize data transfer time. In this paper, we investigate the
  performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  SPM and AFNI), using three neuroimaging datasets of different sizes
  (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  computing clusters. Our results demonstrate that given the features of the
  applications and datasets, Sea provides large speedups (up to 32$\times$) when
  the shared file system's (e.g. Lustre) performance is deteriorated. When the
  shared file system is not overburdened by other users, performance is
  unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  is minimal, as it can be used to limit the number of files created on parallel file systems.
\end{abstract}
\begin{document}

@@

    \centering
    \includegraphics[width=\columnwidth]{figures/sea-diagram.pdf}%
\caption{The Sea data-management library overview}
\label{fig:seaneuro:diagram}
\end{figure*}
    Sea (Figure~\ref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls (more specifically, file access calls to the GNU C library,
    glibc) on Linux systems. This enables Sea to redirect write calls
    aimed at slower storage devices to a faster devices whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini}. This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

@@

    As neuroimaging pipeline results typically require post-processing and
    HPC compute-local resources are only accessible during the reserved
    duration, Sea provides functionality to flush and evict data to persistent
    shared storage. To avoid interrupting ongoing
    processing with data management operations, this is accomplished via a separate thread (known as the
    ``flusher'') that moves data from the caches to long-term storage. Users must inform Sea of files
    that need to be persisted to storage within a file called
    \texttt{.sea\_flushlist}, and temporary files which can be removed from
    cache within a file called the \texttt{.sea\_evictlist}. Both these files
    can be populated using regular expressions to denote the paths to flush and
    evict. If a file occurs in both the \texttt{.sea\_flushlist} and
    \texttt{.sea\_evictlist}, Sea will interpret this as a \texttt{move}
    operation and simply move the file from local to persistent storage rather
    than copying it. Files that will be reused by the application should only be
    flushed rather than flushed and evicted, as files can benefit from speedups
    related to reading from fast rather than slow storage. Sea currently also
    provides a rudimentary prefetch thread that can move files located within
    Sea to the fastest available cache. To use Sea's prefetch
    capabilities, a file called \texttt{.sea\_prefetchlist} needs to be
    populated using regular expressions like the flushing and eviction files.
